---
title: "Variance Reduction for Estimating Value at Risk"
subtitle: "STAT 428 FA2018 - Group #18"
abstract: |
          |This project is focusing on applying methods learned from class in real life financial case. (need adding more sentences)"
author:
  - Haowen Zhou (haowenz4)
  - Qilan Zhang (qilanz2)
  - Jiahui Zhao (jzhao71)
  - Shanxin Zhou (shanxin2)
  - Shuaiqi Zheng (szheng25)
bibliography: bibliography.bib
output: 
  bookdown::pdf_document2
  
always_allow_html: yes
---

```{r set-options, include = FALSE}
# set default code options
knitr::opts_chunk$set(
  # center images
  fig.align = "center", 
  # to display code set to True
  echo = FALSE,
  # suppress message
  message = FALSE,
  # supress warning
  warning = FALSE
)
```

```{r install-and-load-packages, include = FALSE}
# require packages
pkg_list = c('knitr', 'kableExtra', 'magrittr', 'bookdown')
# check install
to_install_pkgs = pkg_list[!(pkg_list %in% installed.packages()[,"Package"])]
# install missing packages
if(length(to_install_pkgs)) {
  install.packages(to_install_pkgs, repos = "https://cloud.r-project.org")
}
# load all packages
sapply(pkg_list, require, character.only = TRUE)
```

<!-- Force a new page -->
\newpage

# Introduction
It is important for banks and insurance companies to estimate and manage the risk to avoid the situation when there is capital deficiency. Value at Risk (VAR) is a measure for the risk of investments loss, which estimates how much value a investment portfolio might lose at given market conditions. Two types of problems are often encompassed by acompany when measuring the risk.The first one is how the value of market risk will change according to risk factors (e.g. interest rate). The other one is what in fluence the risk will pose on the value of a portfolio. This project is intended to develope a model to revalue the portfolio with the interest rate by starting from the simple linear assumption to quadratic model and make use of revalued portfolio to estimate Value at Risk(VAR). The technique problem we are facing is how to make our estimate much more precise,which means we should do variance reduction for our estimator of VAR.

**About the data**

# Methods 

<!-- Force a new page for references -->
\newpage

# Result
# Discussion

<!-- Force a new page for references -->
\newpage

# Conclusion
# Appendix

<!-- Force a new page for references -->
\newpage

# Bibliography

delete the below code when finish
<!-- Force a new page for references -->
\newpage
